\documentclass[12pt,a4paper]{article}

\pdfminorversion=5
\pdfobjcompresslevel=2

\title{Modeling acid-base diodes using COMSOL with MATLAB}

\begin{document}
\maketitle

\section{The model}

\subsection{Acid-base diode}
A gel or membrane connects an alkaline and an acidic reservoir
with electric potential difference between them.
The program computes in 1D the stationary concentration profiles of the ions,
the potential profile in the gel/membrane and the current density.

In this model the diffusion (boundary) layers of the gel are neglected.
The gel/membrane usually contains fixed (not mobile) ions,
which results small jump in the concentrations at liquid-gel boundary.
The applied boundary conditions (Dirichlet) are corrected with this jump
regarding the Donnan equilibrium.

\subsection{Equations}
Poisson--Nernst--Planck (PNP) equations.

The PNP equations are selected in COMSOL using
``Nernst--Planck equation without electroneutrality''
in stationary mode and the ``Poisson-equation''.

\subsection{Restrictions}
The program can handle only one fixed cation and/or one fixed anion
with charges $z=\pm1$. The charge of the mobile ions should be $|z|<3$.

\section{Usage}

\subsection{Start}
\begin{enumerate}
\item Start COMSOL with MATLAB
	(run \verb|comsol matlab| in terminal emulator
	as user \verb|matlab|;
	see the help of COMSOL and MATLAB for possible flags).
\item Change the current directory to
	the location of the acid-base diode program.
\item Run \verb|start_acidbase();| to load the database of
	the existing computed models.
\end{enumerate}

\subsection{Select a model to calculate or to get the results}
\verb|[current,state,fem]=diode_fcn(mode,par,opts);|

Type \verb|help diode_fcn| for details.

\subsection{Plot profiles}
\verb|p_plot(fem,data)|

Type \verb|help p_plot| for details.

\subsection{Plot the current versus any parameter}
\verb|[X,Y]=c_plot(mode,par,var,side)|

Type \verb|help c_plot| for details.

\subsection{Stop}
Run \verb|stop_acidbase();| to save the new or changed models.
Then it is safe to type \verb|exit| or close the MATLAB window.
\end{document}
